Hydra Battles and Cie

### 2021-01-29 doc/chapter-primrec.tex
new lemmas on Ack

You may find also  definition of the Ackermann function and a few  lemmas in
 \href{../theories/ordinals/Prelude/Iterates.html}%
{ordinals.Prelude.Iterates}.

@@

@@

\item Show that for all $n$ and $m$, $A\,n\,m > m$ and  that the functions $A\,n$ are strictly monotonous.
\emph{\textbf{To do.}}

Show also that, for any $n$ and $m$, $A\,n\,m \leq A\,(n+1)\,m$. \emph{\textbf{To do.}}
         Finally, show that for any $n$, $m$ and $k$, 
$A\,k\,(A\,m\,n)\leq A\,(2+\textrm{max}(k,m))\,n$.
\emph{\textbf{To do.}}
\item Show that for any primitive recursive function $f$ of $k$ arguments,
for any $x_1,\dots\,x_k$, $f(x_1,\dots,x_k)\leq A\,n\,(x_1+\dots+x_k)$. \emph{\textbf{To do.}}
\item Show that the Ackermann function is not primitive recursive. \emph{\textbf{To do.}}

@@

\emph{You may start this exercise with
\url{../exercises/primrec/AckermannNotPR.v}.}

>>>>

You may find also  definition of the Ackermann function and a few  lemmas in
 \href{../theories/ordinals/Prelude/Ack.html}%
{ordinals.Prelude.Ack}.

@@

The lemmas which are marked as \textbf{Done} are proved
in the library \texttt{ordinals.Prelude.Ack}.

@@

\item Show that for all $n$ and $m$, $A\,n\,m > m$ and  that the functions $A\,n$ are strictly monotonous.

Show also that, for any $n$ and $m$, $A\,n\,m \leq A\,(n+1)\,m$. 
         Finally, show that for any $n$, $m$ and $k$, 
$A\,k\,(A\,m\,n)\leq A\,(2+\textrm{max}(k,m))\,n$.
\emph{\textbf{Done.}}
\item Show that for any primitive recursive function $f$ of $k$ arguments,
for any $x_1,\dots\,x_k$, $f(x_1,\dots,x_k)\leq A\,n\,(x_1+\dots+x_k)$. \emph{\textbf{Still to do.}}
\item Show that the Ackermann function is not primitive recursive. \emph{\textbf{Still to do.}}

@@

\emph{You may start this exercise with the file
\url{../exercises/primrec/AckermannNotPR.v}.}
